POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2023-10-12 challenges/preliminaries.tex
rework of the common section

We list here some common notions that we will use in the following. Since the calculi under study are somewhat different, we will note in each section which will apply.

@@

The syntax of processes will include:
the process \( \Pend \) or \emph{inaction}, a process which can do nothing. The process \( \Ppar{P}{Q} \) is the \emph{parallel composition} of process \( P \) and process \( Q \).
The two components can proceed independently of each other, or they can interact via shared names.
%The process \( \Pchoice{P}{Q} \) is a non-deterministic \emph{choice} between continuing as the process \( P \) or as the process \( Q \).

>>>>

First, we list some common notions and conventions that we use in the challenges. Since the calculi under study are somewhat different, each section will list the changes that apply.

@@

The syntax of processes includes:
the process \( \Pend \) or \emph{inaction}, a process which can do nothing. The process \( \Ppar{P}{Q} \) is the \emph{parallel composition} of process \( P \) and process \( Q \).
The two components can proceed independently of each other, or they can interact via shared names.
%The process \( \Pchoice{P}{Q} \) is a non-deterministic \emph{choice} between continuing as the process \( P \) or as the process \( Q \).
